---
title: "FFC: Factory Farm Collective"
output: 
  flexdashboard::flex_dashboard:
    social: ["facebook", "twitter","instagram"]
    theme: bootstrap
    orientation: rows
    vertical_layout: fill
    source_code: https://github.com/kbelisar/COVID19-Dashboard-Slaughterhouses
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(dplyr)
library(plotly)
library(ggplot2)
library(DT)
library(mapcan)

FFC <- read.csv("COVID19 Tracking - 2021.csv")

### SUMMARIZE CASES BY PROVINCE
FFC.C <- FFC %>% group_by(province) %>% count(company)
FFC.C <- FFC.C %>% group_by(province) %>% summarize(Companies = sum(n))
FFC.SUM <- FFC %>% group_by(province) %>% summarize(Cases = sum(cases),
                                                    Deaths = sum(deaths, na.rm = T))

FFC.SUM <- merge(FFC.SUM,FFC.C, by = "province")

FFC.SUM$province[FFC.SUM$province=="Ontario"] <- "ON"
FFC.SUM$province[FFC.SUM$province=="British Columbia"] <- "BC"
FFC.SUM$province[FFC.SUM$province=="Alberta"] <- "AB"
FFC.SUM$province[FFC.SUM$province=="Québec"] <- "QC"
FFC.SUM$province[FFC.SUM$province=="Manitoba"] <- "MB"
FFC.SUM$province[FFC.SUM$province=="Nova Scotia"] <- "NS"
FFC.SUM$province[FFC.SUM$province=="Saskatchewan"] <- "SK"

FFC.SUM <- FFC.SUM %>% rename(Province = province)

### SUMMARIZE CASES BY COMPANY [DIFFERENT THAN .R SCRIPT FOR PLOTLY]
FFC.Co <- FFC %>% count(company)
FFC.Co <- FFC.Co %>% group_by(company) %>% summarize(Locations = sum(n))
FFC.COMP <- FFC %>% group_by(province,company) %>% 
  summarize(Cases = sum(cases),Deaths = sum(deaths, na.rm = T))
FFC.COMP$PROP <- (FFC.COMP$Cases/sum(FFC.COMP$Cases))*100

FFC.COMP <- merge(FFC.COMP,FFC.Co, by = "company")

FFC.COMP <- FFC.COMP %>% rename(Company = company, Province = province)

### PROVINCIAL MAP DATA
can.data <- mapcan(boundaries = province,type = standard)
can.data <- inner_join(can.data,FFC.SUM, by = c("pr_alpha" = "Province"))

```

Overview
=======================================================================


Row {data-height=100}
-----------------------------------------------------------------------

### CASES {.value-box}

```{r}
valueBox(sum(FFC$cases), icon = "fas fa-exclamation-circle", caption = "Total Number of Cases", color = "#777777")
```


### DEATHS {.value-box}

```{r}
valueBox(
  value = sum(FFC$deaths, na.rm = T),
  caption = "Total Number of Deaths",
  icon = "fas fa-plus-square",
  color = "#999999"
)
```

### FACILITIES {.value-box}

```{r}
valueBox(sum(FFC$cases>=5), icon = "fas fa-industry", caption = "Facilities with COVID-19 Cases", color = "#BBBBBB")
```

Row
-----------------------------------------------------------------------

### {data-width=670}
```{r map, echo=FALSE}

shinyApp(
  ui = fluidPage(  
    titlePanel("Number of Cases in Canadian Slaughterhouses"),
      plotlyOutput("map")
  ),

server = function(input, output) {

output$map <- renderPlotly({
print(
  ggplotly(can.data %>%
  ggplot(
    aes(x = long, y = lat, group = group,
             fill = Cases, text = paste("Deaths:", Deaths,"\n",
             "Slaughterhouses:",Companies))) +
  geom_polygon() +
  coord_fixed() +
  theme_mapcan() +
    scale_fill_gradient(low = "#E0E0E0", high = "#666666",name = "Cases") +
  theme(plot.title = element_text(hjust = 0, size = 20, face = "bold"),
        plot.subtitle = element_text(hjust = 0, size = 13)))) %>% config(displayModeBar = F)
    })
}

)

```


### {data-width=330}

```{r, echo=FALSE}

## UI
shinyApp(
  ui =fluidPage(    
  titlePanel(""),
    inputPanel(
      selectInput("Province", "Province:", 
                  choices=unique(FFC.COMP$Province))
    ),
    mainPanel(
      plotlyOutput("company.plot")  
    )
  ),
server = function(input, output, session) {
  output$company.plot <- renderPlotly({
    print(
    ggplotly((FFC.COMP %>% filter(Province == input$Province)) %>% ggplot(aes(x = Company, y = Cases,text = paste("Deaths:",Deaths,"\n","Locations:",Locations))) + geom_col(show.legend = FALSE) + theme_classic() + theme(axis.text.x = element_text(angle = 45))))  %>% config(displayModeBar = F) %>% layout(xaxis = list(title = ""), yaxis = list(title = "Cases"))
    })
})



```


Data {data-orientation=columns}
=======================================================================

Column
-----------------------------------------------------------------------

###

```{r data, echo=FALSE}

shinyApp(
    ui = fluidPage(
        fluidRow(
            column(12,
                   DTOutput('table')
            )
        )
    ),
    server = function(input, output) {
        output$table <- renderDT(FFC.COMP,
                                 filter = "top",
                                 options = list(
                                     pageLength = NROW(FFC.COMP)
                                 )
        )
    }
)

```


About
=======================================================================

``` {r, echo=F}
titlePanel("About")
```


#### THE DATA

These data reflect the most recently available data as of January 17th 2021, from the Factory Farm Collective. Available here: https://factoryfarmcollective.ca/covid-19/

#### THE DASHBOARD CREATOR

"With a deep desire to continue to develop my skills as an avid R user and data scientist, I wanted to use my skills to tell the story of slaughterhouse workers who are often members of some of the most vulnerable populations.These populations face various health disparities that intersect with ethnicity, age, gender, and SES".

